%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{0pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Taylor Norton} \\ \vspace{1pt}
    \small (+64) 20 4167 2564 $|$ \href{mailto:taylor.nb@hotmail.com}{\underline{taylor.nb@hotmail.com}} $|$ 
    \href{https://linkedin.com/in/tgnb}{\underline{linkedin.com/in/tgnb}} $|$
    \href{https://github.com/lil-snorts}{\underline{github.com}}
\end{center}
Proven ability to deliver high-quality software and build robust applications, even amid shifting business priorities, by leveraging clear communication, adaptive development practices, and a focus on continuous improvement.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ANZ - Australia and New Zealand Banking Group Limited}{Nov. 2022 -- Present}
      {Software Engineer}{Wellington, NZ}
      \resumeItemListStart
\resumeItem{Built and maintained Java Spring Boot APIs within a microservices architecture to optimize modularity and scalability}
\resumeItem{Implemented Kafka for asynchronous data processing, reducing customer submission times and increasing service reliability by 95\%}
\resumeItem{Automated support request creation to streamline the customer service process and enhance user experience}
        \resumeItem{Verified customer eligibility for endpoint access by validating their details against business rules}
        \resumeItem{Deployed Docker images to OpenShift and managed Jenkins pipelines for streamlined CI/CD processes }
        \resumeItem{Practiced Agile development methodologies as part of a Scrum team}
        \resumeItem{Effectively diagnosed system faults in production}
        \resumeItem{Gave internal presentations of SaaS technologies to business and engineers}
    \resumeItemListEnd      
    \resumeItemListStart
    \resumeItem{Spearheaded the transition from synchronous calls to an EDA using Apache Kafka, enhancing backend performance and client satisfaction.}
    \resumeItem{Developed an Investment Accounts Kafka Consumer to maintain request context across Kafka flows.}
    \resumeItem{Implemented comprehensive integration testing protocols to mitigate risks associated with event consumption failures in Kafka.}
    \resumeItem{Designed and implemented an interceptor bean for Kafka consumers to ensure event traceability and facilitate manual remediation processes.}
    \resumeItem{Led discussions with stakeholders to clarify business rules and requirements for the KiwiSaver Government Contributions feature.}
    \resumeItem{Created API contracts aligning backend capabilities with microservices architecture, ensuring efficient customer request handling.}
    \resumeItem{Identified limitations of current canary deployment patterns for Kafka, proposing a more effective strategy to reduce risk during software updates.}
    \resumeItem{Advocated for necessary changes in response body structure to prevent service failures, enhancing the overall user experience.}
    \resumeItem{Pioneered the migration to HELM chart configurations, simplifying infrastructure management and onboarding processes.}
    \resumeItem{Implemented a web hook for deployment tracking, recommending split responsibilities to enhance security and deployment readiness.}
    \resumeItem{Introduced dynamic API contract cloning to improve code consistency and facilitate accurate service documentation.}
    \resumeItem{Advocated for and implemented the use of builders for test objects, streamlining test creation and standardization.}
    \resumeItem{Collaborated with Product Owner to optimize sprint planning, removing blockers and enabling parallel story development.}
    \resumeItem{Developed and utilized a Splunk dashboard to monitor the Join KiwiSaver feature release, promptly identifying and resolving issues.}
    \resumeItem{Reduced unnecessary debug logging, significantly decreasing log storage costs and improving query performance in Splunk.}
    \resumeItem{Conducted workshops to enhance Splunk proficiency among engineers, showcasing effective usage and analytics capabilities.}
    \resumeItem{Collaborated with API maintainers to gather documentation for legacy systems, ensuring seamless customer data access.}
    \resumeItem{Partnered with architects to design a scalable microservices solution for the Government Contributions feature, aligning with organizational standards.}
\resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{WhatsInTheFridge{\vspace{5pt}}} $|$ \emph{Python, Pandas, BeautifulSoup4, requests}}{}
          \resumeItemListStart
          \resumeItem{WhatsInTheFridge is a web scraping tool designed to suggest recipes based on available ingredients, offering a simple way to minimize food waste}
            \resumeItem{Utilized Python's `requests` and `BeautifulSoup4` libraries for ingredient scraping; stored recipe data using `Pandas` for efficient retrieval}
            \resumeItem{A robots.txt respecting web-scraper script for allrecipes.com}
            \resumeItem{Stores recipes for easy indexing against ingredients the user might have}
            \resumeItem{Used Python libraries 'requests' and 'beautifulsoup4' for scraping ingredients}
            \resumeItem{Managed storage and persistence of recipes and their ingredients using Pandas}
          \resumeItemListEnd
        {\textbf{Fasify-REST-template} $|$ \emph{NodeJs, Fastify, lowdb, chai, mocha}}{}
          \resumeItemListStart
            \resumeItem{Developed a REST server using Fastify, complete with endpoints, schema validation and Error handling}
            \resumeItem{LowDB was used to maintain an in-memory database and write to disk}
          \resumeItemListEnd
        {\textbf{Dictionary-To-JSON-parser} $|$ \emph{Core GoLang, Go}}{}
          \resumeItemListStart
            \resumeItem{Developed a simple Go script to parse the contents of Websters dictionary to JSON format}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, GoLang, Python, SQL (Postgres), HTML/CSS, Shell Scripting} \\
     \textbf{Frameworks}{: Spring Boot, JUnit, Kafka, REST API} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, IntelliJ, Maven, Vim, Linux, Swagger, OpenShift, Jenkins, CI/CD pipelines, Scalable Systems, Code Generation} \\
     \textbf{Libraries}{: Pandas, BeautifulSoup, LowDB, }
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Victoria University of Wellington}{Wellington, NZ}
      {Bachelor of Science in Computer Science}{Sep. 2023}
      
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

